Approximation as Differentiation: Notes

### 2025-05-24 main/framework.tex
Placeholder for Cartesian closure.
Correction to sec 3 intro.

We will consider a pure, total language, where types can be interpreted as sets. Our goal is to equip the
interpretations of programs with Galois connections relating approximations of their inputs to approximations
of their outputs. Since these lattices of approximations depends on the value being approximated, the
semantics of every type $\tau$ must have both a ``conventional'' component, providing the set $X$ associated
with $\tau$, plus an associated lattice of approximations $\partial X(x)$ for every point $x \in X$. The
semantics of an expression $e$ of type $Y$ with a single free variable of type $X$ must then also have two
components: a function $f: X \to Y$ giving the baseline (unapproximated) meaning of the expression, plus a
family of Galois connections $\partial f(x): \partial X(x) \to \partial Y(f(x))$ for every $x \in X$ which can
be used for slicing over that expression.

@@

>>>>

We will consider a pure, total language, where types can be interpreted as sets. Our goal is to equip the
interpretations of programs with Galois connections relating approximations of their inputs to approximations
of their outputs. Since these lattices of approximations depends on the value being approximated, the
semantics of every type $\tau$ must have both a ``conventional'' component, providing the set $X$ which
interprets $\tau$, plus an associated lattice of approximations $\partial X(x)$ for every point $x \in X$. The
semantics of an expression $e$ of type $\sigma$ with a single free variable of type $\tau$ (with $\tau$ and
$\sigma$ conventionally interpreted by $X$ and $Y$) must then also have two components: a function $f: X \to
Y$ giving the conventional interpretation of $e$, and a family of Galois connections $\partial f(x): \partial
X(x) \to \partial Y(f(x))$ for every $x \in X$ which can be used for slicing over that expression.

@@

\subsection{Interpreting higher-order programs}

\todo{conditions under which $\Fam(\cat{C})$ is Cartesian closed, why we need $\PSh_{\CMon}(\cat{C})$, etc}
